\documentclass{cv}

\fullname{Lukas Bjarre}
\doctitle{Cover Letter}
\shortdescription{M.Sc. student in autonomous systems}
\email{lbjarre@kth.se}
\phone{073-252 01 23}
\github{lbjarre}
\linkedin{lukas-bjarre}

\begin{document}

\mainheader

\heading{To whom it may concern,}
My name is Lukas Bjarre and I am currently a M.Sc. student currently writing my thesis at Ericsson Research
within machine intelligence. I am finishin up my thesis and am currently looking to continue to research within this area.

I come from a control theory background but have during the last years of my studies branched out
into machine learning.
My primary interest lies in the intersection of these two areas,
where truly autonomous systems lies capable of decision making based on data driven learning.
Although I've gained a lot of knowledge from my M.Sc. studies I believe that I've only scratched
the surface so far, and wish therefore to continue on with my studies as a Ph.D. candidate.

\sideheading{My strengths}
Assessing my current experience I can highlight some areas I believe
I excel in:
\begin{description}
\item[Wide knowledge background]
    I have a background in electrical engineering, systems theory and machine learning,
    resulting in a good foundation in the intersection of hardware, software, and mathematics.
    I enjoyed my studies but still have a hunger to learn more.
\item[Development experience]
    I have experience in rapid prototype development from various summer internships,
    where smaller hypotheses and research questions where explored through software testing.
    I also care about maintainability and code quality and want my code to be usable outside
    of the initial setting.
\item[Automation mindset]
    Computers are amazing machines and I enjoy finding ways of making
    them do as much of my work as possible. A lazy engineer is an
    efficient engineer, and I believe that my lazy engineering
    practices leads to an highy automated work flow.%
\end{description}

\sideheading{My goals}
Areas in which I want to focus on in the near future are:
\begin{description}
\item[Further my theoretical understanding]
    \parbox[t][][t]{\textwidth}{
    It seems that there is a gap between theoretical findings
    and implementations in machine intelligence systems, and I wish
    to be a part of bridging this gap.
    I find the beauty of mathematical rigor deeply compelling
    and would love to pursue a greater understanding of the
    mathematical concepts behind the subject.}
\item[Work with innovative technology]
    \parbox[t][][t]{\textwidth}{
    I truly believe that machine intelligence is a paradigm-shifting
    technology and I would like nothing more than to be at the forefront
    of the innovations happening in this area.
    My dream would be to develop technology that is pushing the envelope
    of what is possible and to bring it to a larger audience.}
\item[Open source contributions]
    Open source software has benefitted me greatly in my work and I would
    like to pay some tribute back to the community.
    I am going to pursue this goal in my free time but getting paid
    to contribute is a great plus for me.
\item[Develop large scale applications]
    My experience with applications has been limited to smaller projects
    in summer internships and school projects.
    While smaller projects with fast iterations have their advantages
    I would like to gain more experience in seeing how well the concepts
    scale up to large systems.
\end{description}
\vfill
I hope you find my profile of interest and hope to hear back from you soon!%
\\[3mm]
\textit{
    Lukas Bjarre \\
    \today
}
\vfill

\end{document}

