\documentclass{cv}
\input{preamble}
\doctitle{Curriculum Vit\ae}

\newcommand{\msc}{M.Sc.\ }
\newcommand{\bsc}{B.Sc.\ }

\begin{document}

\mainheader

\category{Summary}

Software engineer that thrives in environments with interesting and bold
missions, in a team that wants to find performant and elegant solutions. Experience
in cloud native stacks throughout frontend/backend/infrastructure code.

\category{Work Experience}

\begin{entrywithdates}{Jun 2022}{Current}{Northvolt}
Senior Software Engineer. Developing factory automation systems for Europes
largest battery factory.

\textit{Languages used:} Go, Typescript \\
\textit{Technologies used}: Kubernetes, AWS, Terraform, GraphQL
\end{entrywithdates}

\begin{entrywithdates}{Aug 2021}{May 2022}{Netlight}
Software Consultant. Helped clients with developing Cloud native applications.

\textit{Languages used:} Go \\
\textit{Technologies used}: Kubernetes, AWS
\end{entrywithdates}

\begin{entrywithdates}{Oct 2019}{Aug 2021}{Ericsson}
Data scientist. Working with handling and analysis of in service telecom data
for performance predictions, and development of ML tooling in CloudRAN.

\textit{Languages used:} Python, Javascript, Go, Rust \\
\textit{Technologies used:} Pandas, Scikit learn, Kubernetes, Azure, Argo
\end{entrywithdates}
\begin{entrywithdates}{Feb 2019}{Oct 2019}{Ericsson}
\msc thesis student. Wrote thesis about robust sim-to-reality transfer in deep
reinforcement learning for quadcopter control.

\textit{Languages used:} Python, Julia \\
\textit{Technologies used:} Pytorch, Crazyflie 2.0, rllib
\end{entrywithdates}
\begin{entrywithdates}{May 2018}{July 2018}{Ericsson}
Summer internship. Prototyped sample efficient deep reinforcement learning
methods for virtualized networks functions.

\textit{Languages used:} Python \\
\textit{Technology used:} Pytorch
\end{entrywithdates}
\begin{entrywithdates}{May 2017}{May 2019}{MyAcademy}
Part time job. Tutoring in mathematics for high school students.

\end{entrywithdates}
\begin{entrywithdates}{June 2017}{April 2018}{Scania CV}
Summer internship + part time development engineer. Implemented prototype
software for simulated sensitivity testing in truck engine control systems.

\textit{Languages used:} Python \\
\textit{Techonolgies used:} ZeroMQ
\end{entrywithdates}
\begin{entrywithdates}{June 2016}{July 2016}{Midroc Automation}
Summer internship.
Developed a prototype database tool for a industry 4.0 research project.

\textit{Languages used:} Java, Javascript, HTML, CSS \\
\textit{Technologies used:} MongoDB
\end{entrywithdates}
\begin{entrywithdates}{Aug 2014}{Oct 2014}{KTH}
Part time job. Seminar leader for first year students at university. 
\end{entrywithdates}

\category{Education}

\begin{entrywithdates}{2016}{2019}{KTH}
\msc in Systems, Control \& Robotics.

\textit{Thesis title:} Robust Reinforcement Learning for Quadcopter Control \\
\textit{Topics of interest:} Machine learning, control theory, signal processing
\end{entrywithdates}
\begin{entrywithdates}{2013}{2016}{KTH}
\bsc in Electrical Engineering.

\textit{Thesis title:} Search for Sulfur Emission at Jupiter's Moon Europa \\
\textit{Topics of interest:} Signal processing, computer architecture, optimization
\end{entrywithdates}

\category{Extra Curricular}

\begin{entrywithdates}{June 2017}{May 2018}{Tekniska Högskolans Studenkår}
Member on the Union Council at the Student Union at KTH.
Duties included voting on organisational decisions and
monitoring the executive parts of the union.
\end{entrywithdates}

\begin{entrywithdates}{June 2017}{May 2018}{Konglig Elektrosektionen}
Head of the election comitee of the Electical Engineering chapter at KTH.
Duties included marketing for elected positions,
holding interviews,
and drafting unbiased assessments of candidates.
\end{entrywithdates}

\begin{entrywithdates}{Jan 2017}{May 2018}{Konglig Elektrosektionen}
Auditor of the Electrical Engineering chapter at KTH.
Duties included organisational monitoring of accordance towards charters
and regulations,
as well as economic revision of the organisation (\(\sim1.5\)M SEK turnover).
\end{entrywithdates}

\begin{entrywithdates}{Jan 2016}{Dec 2016}{Konglig Elektrosektionen}
Board member at the Electrical Engineering chapter at KTH.
The position was as head of the student bar,
including responsibilities of planning work for bar personnel,
event planning and marketing,
purchases and stock management for the bar,
and accounting (\(\sim6\)k SEK turnover).
\end{entrywithdates}

\begin{entrywithdates}{Jan 2015}{Dec 2015}{Konglig Elektrosektionen}
Board member at the Electrical Engineering chapter at KTH.
The position held extra responsibility for the chapter's premises.
\end{entrywithdates}

\category{Skills}

\begin{entry}{Programming languages}
    \begin{tabular}[t]{rl}
        \textit{Proficient:}    & Go, Python, Typescript, Rust \\
        \textit{Intermediate:}  & C, SQL, Java, Julia, shell scripting, Lua, \LaTeX \\
        \textit{Familiar:}      & Haskell, Elm, MATLAB, C\#, C\(++\)
    \end{tabular}
\end{entry}
\begin{entry}{Frameworks / tools}
    \begin{tabular}[t]{rl}
        \textit{Containers:}        & Docker, Kubernetes                       \\
        \textit{Infrastructure:}    & Terraform, Terragrunt                    \\
        \textit{Cloud vendors:}     & AWS, Azure                               \\
        \textit{Version control:}   & Git                                      \\
        \textit{CI/CD:}             & Gitlab CI/CD, Github Actions, CircleCI   \\
        \textit{Databases:}         & PostgreSQL, AWS DynamoDB, Redis, MongoDB \\
        \textit{Data science:}      & Pandas, Pytorch, Scikit learn, rllib     \\
        \textit{Web:}               & React, GraphQL                           \\
    \end{tabular}
\end{entry}
\begin{entry}{Languages}
    \begin{tabular}[t]{rl}
        \textit{Native:} & Swedish \\
        \textit{Fluent:} & English \\
    \end{tabular}
\end{entry}

\end{document}
